---
title: "pbc_ric"
author: "Lisa Leung"
date: '2018-01-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Treatment is 	1/2/NA for D-penicillmain, placebo, not randomised

Predicting survival in PBC patients is important for clinical decision making. The
investigators collected data on age as well as baseline laboratory values and clinical
signs including serum bilirubin levels, enlargement of the liver (hepatomegaly),
accumulation of water in the legs (edema), and visible veins in the chest and
shoulders (spiders)—all signs of liver damage.

##only bili (serum bilirunbin) is a continuous variable to measure the disease progress

id:	case number
age:	in years
sex:	m/f
trt:	1/2/NA for D-penicillmain, placebo, not randomised
time:	number of days between registration and the earlier of death,
transplantion, or study analysis in July, 1986
status:	status at endpoint, 0/1/2 for censored, transplant, dead
day:	number of days between enrollment and this visit date

all measurements below refer to this date

albumin:	serum albumin (mg/dl)
alk.phos:	alkaline phosphotase (U/liter)
ascites:	presence of ascites
ast:	aspartate aminotransferase, once called SGOT (U/ml)
bili:	serum bilirunbin (mg/dl)
chol:	serum cholesterol (mg/dl)
copper:	urine copper (ug/day)
edema:	0 no edema, 0.5 untreated or successfully treated
1 edema despite diuretic therapy
hepato:	presence of hepatomegaly or enlarged liver
platelet:	platelet count
protime:	standardised blood clotting time
spiders:	blood vessel malformations in the skin
stage:	histologic stage of disease (needs biopsy)
trig:	triglycerides (mg/dl)

```{r pbc}
#https://stat.ethz.ch/R-manual/R-devel/library/survival/html/pbcseq.html
library(survival)
library(tidyverse)
pbcseq
summary(pbcseq$day)
dim(na.omit(pbcseq))
dim(pbcseq)

table(pbcseq$status)

data <- pbcseq

data$trt <- as.factor(data$trt)
data$status <- as.factor(data$status)
data$hepato <- as.factor(data$hepato)
data$edema <- as.factor(data$edema)

latest_date <- data %>% group_by(id) %>% summarise(max_day=max(day))
last_data <- left_join(latest_date, data, by = c("id"="id","max_day"="day"))

no_0_data <- last_data[last_data$max_day!=0,]
no_0_data <- no_0_data[no_0_data$status!=1,]

names(no_0_data)

plot(no_0_data$max_day)
plot(no_0_data$bili)
plot(no_0_data$bili,no_0_data$max_day)

table(no_0_data$trt,no_0_data$status)
plot(no_0_data$trt,no_0_data$hepato)
plot(no_0_data$trt,no_0_data$edema)

plot(no_0_data$trt,no_0_data$bili)
## can't seem to find anything on a dataset that only uses the very last observation on each subject....will try the slope of bilirum values on regression levels or something like that
```

```{r}
#d<-data[data$id==100,]
#day<-d$day
#bili<-d$bili
#coef(lm(bili~day))[2]
#summary(lm(bili~day))

lin_function <- function(x,y){
  lm1 <- lm(y ~ x)
  return(coef(lm1)[2])
}

avg_data <- data %>% group_by(id) %>% summarise(avg_bili = lin_function(day, bili), )
last_data <- left_join(avg_data, data, by = c("id"="id"))
last_data

ok <- last_data[,names(last_data) %in% c("id", "avg_bili", "trt")] 
do_this<-unique(ok)
plot(do_this$trt, do_this$avg_bili)
summary(lm(avg_bili~trt, data=do_this))
```

