---
title: "Simulation_cide_RIC_poisson"
author: "Lisa Leung"
date: '2018-01-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library}
library(DescTools)
library(data.table)
```


```{r RIC_curve}
RIC_curve <- function(mat, marker, benefit){
  
  proportion <- seq(0, 1, by = 0.01)
  
  #Finding marker values by creating a new data set with trt = 0....
  no_trt_data <- as.data.frame(cbind(mat[,!names(mat) %in% trt], trt = 0))
  colnames(no_trt_data)[colnames(no_trt_data) == 'trt'] <- trt
  trt<-"trt"
  #Construct marker values when trt = 0
  marker <- predict(lm1, newdata = no_trt_data)
  
  #Creating data set that has all trt variable as 1
  all_trt_data <- as.data.frame(cbind(mat[,!names(mat) %in% trt], trt = 1))
  colnames(all_trt_data)[colnames(all_trt_data) == 'trt'] <- trt
  
  #Construct marker values when trt = 0
  y_all_trt <- predict(lm1, newdata = all_trt_data)

  #Grabbing biomarker threshold such that it matches the proportion, in this case, our biomarker is y_no_trt
  k <- quantile(marker, probs = 1 - proportion)
  
  #Creating treatment vectors such that patients are assigned to treatment if biomarker is greater than threshold
  new_trt <- sapply(k, function (x) as.numeric(marker > x))
  
  #relative benefit
  b1 = apply(new_trt, 2, function(x) sum((y_all_trt - y_no_trt)*x)/
               sum(y_all_trt - y_no_trt))
  
  #return the vector of relative benefit
  b1
  
}

```
##SIMULATION: Will return a vector of AUCs

auc_vec: returns a vector of AUC
x1 and x2: covariates
e: normally distributed errors
trt: assume that treatment was randomly assigned (for original data, we don't know our treatment yet before the biomarker values)
bio: biomarkers
ben: beneficial values after treatment
y:poisson outcome (not necessarily biomarker values OR beneficial values!!)
mat1: dataframe including covariates, treatment, and outcome y

```{r initialize}
n = 100
int <- 0.5
b1 <- 2
b2 <- 3.5
b3 <- 2
b4 <- 5
```

```{r simulation}
auc_vec<-c()
i=1
for (i in 1: 1000){

set.seed(i)
x1 <- runif(n, 0, 10)
x2 <- rnorm(n, 10, 6)
trt <- rbinom(n, size=1, prob=0.5)
bio <- rpois(n, b1*x1 + b2*x2)
ben <- rpois(n, b3*trt + I(b4*trt*x2))
y <- rpois(n, int + b1*x1 + b2*x2 + b3*trt + I(b4*trt*x2))
mat1 = data.frame(x1=x1, x2=x2, trt=trt, y=y)

##According to the case study, they first found a model including the treatment assignment and the clinical variables. 
#This is labeled as a "Q model"

#Poisson
glm1 <- glm(y ~ x1 + x2 + trt + I(trt*x2), family = "poisson", data=mat1)

#CALCULATING AUC
ric_y <- RIC_exp(ric_x, mat1, 'trt', 'y', lm1)
auc_vec <- append(auc_vec, AUC(ric_x,ric_y))

cat("Done:", i,"\n")
}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
